Computing the bicharacter of huge subspaces of polynomials

### 2019-07-24 article/article.tex
Correct other tense mistakes.

	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}). Therefore, when the precision is not necessary, we will drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.

@@

	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\Elambdar{\lambda}{r}$ is not easy to compute due to the dimension but hopefully most of the strategies we used to compute the character of $\harmonics_{n}^{(r)}$ work for $\Elambdar{\lambda}{r}$.

@@

	We presented in the previous examples all the steps of the computation using or not different strategies to optimize the computations. Thus, the code can be easily adapted to other generators and other operators (see section \ref{section_futher_work} for examples) at each step.

>>>>

	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}). Therefore, when the precision is not necessary, we drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.

@@

	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\Elambdar{\lambda}{r}$ is not easy to compute due to the dimension but hopefully most of the strategies we use to compute the character of $\harmonics_{n}^{(r)}$ work for $\Elambdar{\lambda}{r}$.

@@

	We presente in the previous examples all the steps of the computation using or not different strategies to optimize the computations. Thus, the code can be easily adapted to other generators and other operators (see section \ref{section_futher_work} for examples) at each step.
